Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-07-01 paper/src/5_evaluation.tex
finish evaluation

In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region%, using
Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, since when we use I/O burst buffer, read and write throughput are the same, both is equal to throughput between computing nodes and I/O nodes, for using I/O burst buffer, we use this throughput value.
%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
%m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}. Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
%According to these data and definition described above, we use values defined below.

@@

First we compare the I/O throughput between direct connection and I/O burst buffer (both cache miss and cache hit) on TSUBAME and Amazon EC2.

@@

However 100\% cache hit is a ideal condition not pratical, so in Fig.~\ref{throughput cache rate}, we also show predict throughput for 75\%,50\% and 25\% cache hit.
When there is a cache miss both in read and write, data need to be transfer via both Ethernet and Internet like 0\% cache hit case, and for cache hit, files can be read and written via Ethernet like 100\% cache hit case, so we use two-side Internet throughput($thr_I$) shown in Fig.~\ref{point to point connection LAB}, Ethernet throughput in Amazon($thr_E$) shown in Fig.~\ref{point to point connection AMAZON} and following formular to evaluate throughput for each cache hit rate.

@@

and result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between Ethernet bandwidth and Internet bandwidth, also data can transfer faster in Ethernet, user application must wait until cache miss data transferred through Internet.

@@

Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time, 
As we showed, By using I/O burst buffer, we can achieve a high I/o throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
\[\frac{Data~size}{throughput}*cost*node\]
According to Amazon pricing policy, m3.xlarge instance is charged \$0.405 for each hour usage in Asia Pacific(Tokyo).

Fig.~\ref{cost} shows cost comparison between each cache hit rate and direct I/O, which read or write 100GB data, we can see that cost
%Since we assume number of I/O buffer node increases as number of computing nodes increases, 
%After that, we compare overall cost when use two-side buffer and one-side buffer, since execution time, in our case, I/O time and I/O throughput will affect cost, for Internet and Ethernet throughput, we use. 
%From Fig.~\ref{cost},

>>>>

In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region.%, using
Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, we compare I/O througput and overall cost between direct I/O and I/O burst buffer with different cache hit rate, here cache hit rate means the percentage of data in total I/O is buffered in buffer queue or the percentage of data can write to buffer queue before queue becomes full.
since when we use I/O burst buffer, read and write throughput are the same, both is equal to throughput between computing nodes and I/O nodes, for using I/O burst buffer, we use this throughput value.
%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
%m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}. Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
%According to these data and definition described above, we use values defined below.

@@

First we compare the I/O throughput between direct connection and I/O burst buffer (both cache miss and cache hit) on TSUBAME and Amazon EC2.
In this simulation we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum Ethernet throughput.
In practice, I/O buffer nodes may have a better Ethernet condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, Ethernet bandwidth also can be fully utilized.

@@

However 100\% cache hit is a ideal condition not pratical, so in Fig.~\ref{throughput cache rate}, we also show predict throughput for 75\%,50\% and 25\% cache hit rate.
When there is a cache miss both in read and write, data need to be transfer via both Ethernet and Internet like 0\% cache hit case, and for cache hit, files can be read and written via Ethernet like 100\% cache hit case, so we use two-side Internet throughput($thr_I$) shown in Fig.~\ref{point to point connection LAB}, Ethernet throughput in Amazon($thr_E$) shown in Fig.~\ref{point to point connection AMAZON} and following formular to evaluate throughput for each cache hit rate.

@@

Result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between Ethernet bandwidth and Internet bandwidth, also data can transfer faster in Ethernet, user application must wait until cache miss data transferred through Internet.

@@

Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time, 
As we showed, By using I/O burst buffer, we can achieve a high I/o throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
\[cost=\frac{Data~size}{throughput}\times cost\times node\]
According to Amazon pricing policy, m3.xlarge instance is charged \$0.405 for each hour usage in Asia Pacific(Tokyo).
For direct I/O, nodes is equal to number of computing nodes, but for I/O burst buffer, since we assume that number of I/O nodes is equal to number of computing nodes, here the value of node in above formular will be 2 times number of computing nodes.

Fig.~\ref{cost} shows cost comparison between each cache hit rate and direct I/O, which read or write 100GB data, we can see that cost grows as number of nodes grows, except for 100\% cache hit, which throughput is proportional to nodes number.
As the Fig.~\ref{cost} shows, if cache hit rate is higher than 50\%, the overall cost using I/O burst buffer will lower than direct I/O, however, if cache hit rate is lower than 50\%, using I/O burst buffer will cost more.

From above simulations, we can see that if we can achieve a high cache hit rate, we can achieve a high throughput up to 4-20 times faster than direct I/O as well as a low cost up to 2-12 times lower than direct I/O for 20 client nodes.
It is may be difficult for read data cache hit rate to be higher than 50\% (can be possible according to data locality), but it is reasonable for write data can be buffered in buffer queue, since public clouds usually provide instance with large size of memory, and it is easy to achieve a Tera size of buffer queue.
%Since we assume number of I/O buffer node increases as number of computing nodes increases, 
%After that, we compare overall cost when use two-side buffer and one-side buffer, since execution time, in our case, I/O time and I/O throughput will affect cost, for Internet and Ethernet throughput, we use. 
%From Fig.~\ref{cost},
